Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-07 paper/manuscript.tex
broken overleaf will debug locally

When starting an alchemical free energy project you need to determine if an alchemical free energy calculation is the appropriate strategy by initially counting the cost of your
project: Can you even hope to tackle the problem with available resources and, if successful, will it
be worth it?
\subsection*{How accurate are alchemical free energy calculations?}

@@

\subsection*{How reproducible are alchemical free energy calculations?}

@@

\subsection*{Is my problem suitable for alchemical free energy calculations?}
Before even planning free energy calculations to study binding to a
particular target, it is important to assess what is known about the
system and its timescales and its suitability for free energy
calculations, as well as the \emph{purpose} of the calculations and
the amount of available computer resources. In some cases, predicting
accurate binding free energies for a particular target might be a
\emph{more} challenging effort than simply measuring them! This is
often the case when dealing with database screening problems, where
compounds might be easily and quickly available commercially for
testing and free energy calculations could consume a much larger
amount of resources. Free energy calculations thus typically only
appeal when (slow or costly) synthesis would be required to do
experiments or experiments are otherwise cost-prohibitive.

@@

\subsection*{Is the expected accuracy of the computation sufficient?}
The requisite level of accuracy is another important consideration ---if the
goal is to guide lead optimization when many compounds will be
synthesized, free energy calculations can be appealing even with
accuracy in the 1--2 kcal/mol range~\cite{mobley2012perspective}, but if the number of compounds to be synthesized is very small, this accuracy may not be enough to provide
much value.

Here we include a simple estimate of the value provided by alchemical
free energy calculations in lead optimization.  Let $P(\Delta\Delta
G)$ be the probability distribution of the changes in the binding free
energies of a new set of molecules during one round of lead
optimization, and let $P(\Delta\Delta G^\dagger|\Delta\Delta G)$ be the
conditional probability of the binding free energy change computed by
the free energy calculations, $\Delta\Delta G^\dagger$, given the actual
change $\Delta\Delta G$.  The latter conditional probability can be modeled
by a normal distribution
\begin{equation}
  P(\Delta\Delta G^\dagger|\Delta\Delta G) = \frac{1}{\sqrt{2\pi\sigma^2}}
  \exp\left(-\frac{(\Delta\Delta G^\dagger - \Delta\Delta G)^2}{2\sigma^2}\right),
  \label{eqn:free-energy-distribution}
\end{equation}
where $\sigma$ signifies the accuracy of free energy calculations.
Here we assume that there is no systematic bias in the free energy
calculations, i.e., on average, the free energy change computed by
free energy calculations agrees with the actual free energy change.
%
In lead optimization guided by free energy calculations, we only
synthesize and experimentally test molecules that are predicted to
have favorable free energy changes.  We are thus interested in how
often that a molecule predicted to bind stronger actually turns out to
bind stronger.  In other words, we are interested in the conditional
probability:
\begin{equation}
  P(\Delta\Delta G<0|\Delta\Delta G^\dagger<0).
  \label{eqn:true-positive}
\end{equation}
%
For illustrative purposes, we assume that the actual changes in the
binding free energies for a set of new molecules also follow normal
distribution, that the standard deviation in the changes is $RT\ln 5$
(corresponding to a 5-fold change in the binding affinities), and that
1 in 10 new molecules have increased binding affinity ($\Delta\Delta G
\leq 0$).  Under such assumptions, the conditional probability in
Eq.~\ref{eqn:true-positive} can be easily computed.  If the accuracy
of free energy calculations is $\sigma = 1$ kcal/mol, $P(\Delta\Delta
G<0|\Delta\Delta G^\dagger<0) = 0.35$, which means that out of every
10 molecules selected for predicted favorable free energy change, on
average 3.5 molecules will have actual favorable free energy change.
In other words, selection by free energy calculations yields 3.5 times
more molecules of improved affinities than selection without free
energy calculations.
%  
Available computational resources and timescales of motion also factor
into this initial analysis. An individual free energy calculation
involves simulations at many different intermediate states (perhaps
20-40 or more) and each of these must typically be long enough to
capture the relevant motions in the system. If such motions are
microsecond events or longer, the computational cost of running 20-40
microsecond or longer simulations for each of $N$ ligands may become
prohibitive, or at least should be carefully considered. 
%
\subsection*{Can I afford the calculation?}
Furthermore, are available computational resources sufficient that throughput will be
reasonable compared to needs of experimental collaborators working on
this system? How many ligands ($N$) can you afford to handle given
your computational resources? As cloud computing becomes more available, in-house GPU clusters may not be necessary if calculations are not run on a regular basis.
This analysis should be done up front, part of ``counting the cost''
of involvement in a particular project. In some cases, the analysis may conclude that free energy calculations will not be feasible for the proposed problem.
\todo[inline, color={green!20}]{ASJSM: @everyone: Might be nice to do an example calculation X perturbation on GTX 1080s on a AWS cluster cost \$\$X. Synthesis costs \$\$Y. }

Here, by ``cost'', we refer not just to financial cost of the calculations relative to experiments, but also time -- can the calculations can be run faster than experiments are done? How will the relevant resource and opportunity costs factor in? Both computation and experiment require human time, supplies (of different sorts), and equipment. In the extreme limit, for example, it would not make sense to spend a month running a binding free energy calculation if the equivalent experiment could be done in a day with resources already on hand. Such issues should be considered before deciding to conduct binding free energy calculations.
%
\subsection*{Is an exploratory study what I want?}
An additional consideration is how much is known about your particular
target, ligand binding modes in the target, and any relevant motions
-- essentially, has it been studied enough to know whether it might be
suitable for free energy calculations? It is important to know if the system has hardly been studied, because should the initial calculations perform poorly, the effort may turn into an attempt to understand the relevant sampling, force field, or system preparation problems.
%
If you are unsure whether your project is feasible, one option may be
to conduct a short exploratory study to assess tractability for just a very small
number of ligands. This can be sufficient to get an initial
idea of feasibility and accuracy of the calculations for the
proposed target.

@@

\subsection*{Capturing the experimental conditions}

@@

\subsection*{Is my binding mode accurate?}

@@

\subsection*{Input setup and scale of calculations}

@@

Running binding FE calculations in a drug discovery application will typically require the use of software or tools to facilitate the calculations of many compounds. The commercial implementation from Schr\"{o}dinger, FEP+, uses a graphical user interface and once the user has calculated any missing force field parameters, calculations can be prepared and submitted within minutes. The software builds the network of perturbations, connecting similar compounds based on LOMAP methodology~\cite{liu2013lead}, all inputs for the Desmond simulations are built automatically and the job can be saved or run immediately on available GPUs. The cost of this software is often prohibitive but alternative tools are becoming available to allow relatively straight forward running of alchemical FE calculations with other software~\cite{gapsys2015pmx, loeffler2015fesetup} (CITE https://pubs.acs.org/doi/full/10.1021/acs.jcim.9b00105, cite https://pubs.rsc.org/en/content/articlehtml/2020/sc/c9sc03754c, cite https://pubs.acs.org/doi/abs/10.1021/acs.jcim.5b00368, cite https://jcheminf.biomedcentral.com/articles/10.1186/s13321-019-0348-5). One consideration at this point is to define the perturbations suitable for the application. For instance, if the goal is to accurately assess the relative binding energy of a small number of compounds, possibly with challenging synthesis, the map of perturbations may contain as many connections between compounds as affordable. However, when running calculations on hundreds of compounds a so called ‘star-map’ can be used that just contains one connection per compound: perturbing every compound to a central ligand, typically the crystal structure ligand (CITE https://pubs.acs.org/doi/abs/10.1021/acs.jcim.9b00367). In this way the top-ranking examples can be readily identified and submitted to additional calculations in a second round. 
%
\subsection*{Making predictions, understanding errors}
For prospective drug discovery applications there are several other considerations including understanding likely errors and taking selection bias into account. It is crucial when proposing compounds for synthesis to have some idea of the underlying error or uncertainty in the predictions. A retrospective assessment can give an indication of prospective performance for similar molecules (CITE https://pubs.acs.org/doi/abs/10.1021/acs.jcim.6b00220). Beyond this, several parameters provide useful indicators of performance, results suggest MBAR errors for perturbations greater than 0.3 kcal/mol can be indicative of inaccuracy~\cite{perez-benito2019predicting}. In addition, the hysteresis can be checked by comparing the difference for forward and reverse perturbations of the same structural change, or in the case of large maps of perturbations cycle closure hysteresis~\cite{wang2013modeling} indicates problematic perturbations involved in cycles connecting many compounds. Selection bias, as described above, can be problematic in prospective applications as there is normally an aim to focus on only a narrow range of predicted activity (i.e. the most active). Thus, correlation between prediction and subsequent experiment may lead to disappointment but corrections can be applied based on previous recommendations~\cite{abel2017critical}. 
%

@@

%
%
%
%%%%%%%%%%%%
% Step 1   %
%%%%%%%%%%%%
%
\section{What simulation protocol should I choose? -- Step 2}
\label{sec:step2}
Alchemical free energy calculations can be grouped into two main categories, ``absolute'' (\ref{fig:fig_absolute_thermodynamic_cycle}) and ``relative'' \footnote{The distinction is a bit of a misnomer, since both compute ratios of partition functions relative to another state, and neither computes an absolute free energy.}(\ref{fig:fig_binding_thermodynamic_cycle}), which differ in whether they compute properties for a single molecule (absolute) or compare properties of different, usually closely related, molecules (relative).
To use binding as a concrete example, in absolute binding free energy calculations, one computes the binding free energy of a ligand to an individual receptor relative to a standard reference concentration.
In contrast, in relative binding free energy calculations, one compares the binding free energy of two related inhibitors to determine the potency difference.
\subsection*{Absolute and relative free energy calculations have some differences}
Many of the issues of setup and protocol for alchemical calculations are common, but some are different between absolute and relative calculations, so before treating the common elements we consider the protocol differences.

\subsubsection*{Choices unique to relative free energy calculations}

@@

\subsubsection*{Absolute free energy calculations must handle the standard state and use restraints}
\label{sec:standardstate-restraints}

@@

\subsection*{Absolute and relative calculations must deal with some of the same issues}

\subsubsection*{Structural definition of the bound state and weak binders}
\todo[inline, color={green!20}]{ASJM: This a bit waffly. What are the recommendations, of how to setup these restraints?}

@@

\subsubsection*{Changes in net charge can be challenging/problematic.}

@@

\subsubsection*{The importance of the alchemical pathway\label{sec:important_path}}
\todo[inline, color={green!20}]{ASJM: This a bit waffly. Can we address: what do softcore potentials actually look like (equation)? Give an example of a lambda switching function(equation)? MRS: adressed these questions to some extent.  How should you chose your lambda intermediates? What is the best practice here? I have conveniently provided a figure to help with the discussion.}
\todo[inline, color={red!40}]{LNN: write common principles alchemical path choice. MRS: mostly wrote this, LNN can comment on it,}
\todo[inline, color={red!40}]{AR: write absolute-specific section on  alchemical path choice}
\todo[inline, color={red!40}]{BA: write relative-specific section on  alchemical path choice}

@@

\subsubsection*{What different sampling schemes exist and which one should I use?}
\todo[inline, color={green!20}]{ASJSM: I'll expand on this}
\ref{fig:fig_sampling_scheme} A:\cite{hedges2019biosimspace, song2019using } B\cite{aldeghi2015accurate, wang2015accurate,jiang2019computing} C:\cite{li2007simulated, tan2017optimally} D:\cite{aldeghi2018accurate}
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig8_sampl_scheme/Figure.pdf}
    \caption{\textbf{Four sampling strategies available in different software packages.} A: Multiple replicas in parallel at different lambda states. B: Hamiltonian replica exchange scheme. C: Single replica scheme sampling from all $\lambda$ states. D: Non-equilibrium sampling scheme.}
    \label{fig:fig_sampling_scheme}
\end{figure}

\subsubsection*{How long should I run my simulation for and what information should be saved?}

@@

A simple, but effective, way of checking for convergence is to compute the same property by multiple estimators. 
The uncertainty in the free energy, for example, has multiple ways to be estimated, e.g. through standard error propagation methods (including MBAR's estimator, which is based on the same principles as standard error propagation), through bootstrap methods, through multiple independent runs, etc. 
Independent of how the property is estimated, its important to remember that they are \textit{estimations of the property}, not the true underlying property itself. 
These estimators are usually consistent estimators, meaning they will converge to the true answer in the limit of sufficient sampling, not necessarily unbiased ones though.
As such, it is a good idea to subject different estimators to the same data to see if they yield either the same estimate (within error and bias), or if they fluctuate wildly. 
This is not a perfect method as some estimators, such as exponential averaging, will converge significantly more slowely, relative to more accurate estimators like MBAR. 
Therefore, it is a good idea to apply the estimators to different fractions of the data to see if the main estimator of free energy you have chosen is stable.

@@

\subsection*{Detecting the boundary between equilibrated and production regions}
\label{sec:automatic-equilibration-detection}

@@

\subsection*{Decorrelating samples for analysis}
\label{sec:decorrelating-samples}

@@

\subsection*{Estimators for free energy differences}

@@

\subsubsection*{Uncertainty estimation}

@@

In addition to statistical uncertainty and sampling, a variety of other factors can impact results from binding free energy calculations. In addition to the choice of initial configuration, results can depend on the choice of force field for the protein/receptor, water, and small molecuel(s), so rerunning calculations with different choices of force field can also be used to assess how sensitive results and conclusions are to these particular choices. Other factors, like system preparation (choice of protonation state, tautomer, counterion presence, salt concentration, etc.) can also substantially impact results~\cite{10.1146/annurev-biophys-070816-033654, https://escholarship.org/uc/item/9p37m6bq#main}, so unless modelers are confident they have these factors correct, sensitivity to these choices may also need to be examined.

\subsubsection*{Are my simulations any good?}
One way of assessing reliability of the calculations is checking the phase space overlap between neighboring $\lambda$-windows~\cite{wu2005phasespace,wu2005phasespacea}. For this purpose, a so-called overlap matrix can be used. This is a $K\times K$ matrix, where $K$ is the number of simulated states, i.e. $\lambda$s. Sufficient overlap is important for reweighting estimators such as BAR or MBAR, but cannot help assess reliability of estimates, when using TI. 
These matrices are graphical representations of the phase space overlap, i.e. the average probability that a sample generated at state $j$ can be observed at state $i$. As this probability is computed considering the samples from all states (and not just the adjacent states), the values in each row and column add up to 1. In this analysis, the goal is to ensure every state has overlap with its neighbors in both directions -- so that off-diagonal elements are significantly larger than zero. Usually this means the matrix should be at least tridiagonal.

@@

\subsection*{Best practices for data representation}

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} 
JS: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.
MK: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.
DLM: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.
GT: Contributed to introduction and drug discovery sections, and helped edit the paper.
AR: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:step2}, and helped edit the paper.
MRS: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations, 
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

>>>>

When starting an alchemical free energy project you need to determine if an alchemical free energy calculation is the appropriate strategy by initially counting the cost of your
project: Can you even hope to tackle the problem with available resources and, if successful, will it
be worth it?
\subsection{How accurate are alchemical free energy calculations?}

@@

\subsection{How reproducible are alchemical free energy calculations?}

@@

\subsection{Is my problem suitable for alchemical free energy calculations?}
Before even planning free energy calculations to study binding to a
particular target, it is important to assess what is known about the
system and its timescales and its suitability for free energy
calculations, as well as the \emph{purpose} of the calculations and
the amount of available computer resources. In some cases, predicting
accurate binding free energies for a particular target might be a
\emph{more} challenging effort than simply measuring them! This is
often the case when dealing with database screening problems, where
compounds might be easily and quickly available commercially for
testing and free energy calculations could consume a much larger
amount of resources. Free energy calculations thus typically only
appeal when (slow or costly) synthesis would be required to do
experiments or experiments are otherwise cost-prohibitive.

@@

\subsection{Is the expected accuracy of the computation sufficient?}
The requisite level of accuracy is another important consideration ---if the
goal is to guide lead optimization when many compounds will be
synthesized, free energy calculations can be appealing even with
accuracy in the 1--2 kcal/mol range~\cite{mobley2012perspective}, but if the number of compounds to be synthesized is very small, this accuracy may not be enough to provide
much value.

Here we include a simple estimate of the value provided by alchemical
free energy calculations in lead optimization.  Let $P(\Delta\Delta
G)$ be the probability distribution of the changes in the binding free
energies of a new set of molecules during one round of lead
optimization, and let $P(\Delta\Delta G^\dagger|\Delta\Delta G)$ be the
conditional probability of the binding free energy change computed by
the free energy calculations, $\Delta\Delta G^\dagger$, given the actual
change $\Delta\Delta G$.  The latter conditional probability can be modeled
by a normal distribution
\begin{equation}
  P(\Delta\Delta G^\dagger|\Delta\Delta G) = \frac{1}{\sqrt{2\pi\sigma^2}}
  \exp\left(-\frac{(\Delta\Delta G^\dagger - \Delta\Delta G)^2}{2\sigma^2}\right),
  \label{eqn:free-energy-distribution}
\end{equation}
where $\sigma$ signifies the accuracy of free energy calculations.
Here we assume that there is no systematic bias in the free energy
calculations, i.e., on average, the free energy change computed by
free energy calculations agrees with the actual free energy change.
%
In lead optimization guided by free energy calculations, we only
synthesize and experimentally test molecules that are predicted to
have favorable free energy changes.  We are thus interested in how
often that a molecule predicted to bind stronger actually turns out to
bind stronger.  In other words, we are interested in the conditional
probability:
\begin{equation}
  P(\Delta\Delta G<0|\Delta\Delta G^\dagger<0).
  \label{eqn:true-positive}
\end{equation}
%
For illustrative purposes, we assume that the actual changes in the
binding free energies for a set of new molecules also follow normal
distribution, that the standard deviation in the changes is $RT\ln 5$
(corresponding to a 5-fold change in the binding affinities), and that
1 in 10 new molecules have increased binding affinity ($\Delta\Delta G
\leq 0$).  Under such assumptions, the conditional probability in
Eq.~\ref{eqn:true-positive} can be easily computed.  If the accuracy
of free energy calculations is $\sigma = 1$ kcal/mol, $P(\Delta\Delta
G<0|\Delta\Delta G^\dagger<0) = 0.35$, which means that out of every
10 molecules selected for predicted favorable free energy change, on
average 3.5 molecules will have actual favorable free energy change.
In other words, selection by free energy calculations yields 3.5 times
more molecules of improved affinities than selection without free
energy calculations.
%  
Available computational resources and timescales of motion also factor
into this initial analysis. An individual free energy calculation
involves simulations at many different intermediate states (perhaps
20-40 or more) and each of these must typically be long enough to
capture the relevant motions in the system. If such motions are
microsecond events or longer, the computational cost of running 20-40
microsecond or longer simulations for each of $N$ ligands may become
prohibitive, or at least should be carefully considered. 
%
\subsection{Can I afford the calculation?}
Furthermore, are available computational resources sufficient that throughput will be
reasonable compared to needs of experimental collaborators working on
this system? How many ligands ($N$) can you afford to handle given
your computational resources? As cloud computing becomes more available, in-house GPU clusters may not be necessary if calculations are not run on a regular basis.
This analysis should be done up front, part of ``counting the cost''
of involvement in a particular project. In some cases, the analysis may conclude that free energy calculations will not be feasible for the proposed problem.
\todo[inline, color={green!20}]{ASJSM: @everyone: Might be nice to do an example calculation X perturbation on GTX 1080s on a AWS cluster cost \$\$X. Synthesis costs \$\$Y. }

Here, by ``cost'', we refer not just to financial cost of the calculations relative to experiments, but also time -- can the calculations can be run faster than experiments are done? How will the relevant resource and opportunity costs factor in? Both computation and experiment require human time, supplies (of different sorts), and equipment. In the extreme limit, for example, it would not make sense to spend a month running a binding free energy calculation if the equivalent experiment could be done in a day with resources already on hand. Such issues should be considered before deciding to conduct binding free energy calculations.
%
\subsection{Is an exploratory study what I want?}
An additional consideration is how much is known about your particular
target, ligand binding modes in the target, and any relevant motions
-- essentially, has it been studied enough to know whether it might be
suitable for free energy calculations? It is important to know if the system has hardly been studied, because should the initial calculations perform poorly, the effort may turn into an attempt to understand the relevant sampling, force field, or system preparation problems.
%
If you are unsure whether your project is feasible, one option may be
to conduct a short exploratory study to assess tractability for just a very small
number of ligands. This can be sufficient to get an initial
idea of feasibility and accuracy of the calculations for the
proposed target.

@@

\subsection{Capturing the experimental conditions}

@@

\subsection{Is my binding mode accurate?}

@@

\subsection{Input setup and scale of calculations}

@@

Running binding FE calculations in a drug discovery application will typically require the use of software or tools to facilitate the calculations of many compounds. The commercial implementation from Schr\"{o}dinger, FEP+, uses a graphical user interface and once the user has calculated any missing force field parameters, calculations can be prepared and submitted within minutes. The software builds the network of perturbations, connecting similar compounds based on LOMAP methodology~\cite{liu2013lead}, all inputs for the Desmond simulations are built automatically and the job can be saved or run immediately on available GPUs. The cost of this software is often prohibitive but alternative tools are becoming available to allow relatively straight forward running of alchemical FE calculations with other software~\cite{gapsys2015pmx, loeffler2015fesetup} (CITE https://pubs.acs.org/doi/full/10.1021/acs.jcim.9b00105, cite https://pubs.rsc.org/en/content/articlehtml/2020/sc/c9sc03754c, cite https://pubs.acs.org/doi/abs/10.1021/acs.jcim.5b00368, cite https://jcheminf.biomedcentral.com/articles/10.1186/s13321-019-0348-5). One consideration at this point is to define the perturbations suitable for the application. For instance, if the goal is to accurately assess the relative binding energy of a small number of compounds, possibly with challenging synthesis, the map of perturbations may contain as many connections between compounds as affordable. However, when running calculations on hundreds of compounds a so called ‘star-map’ can be used that just contains one connection per compound: perturbing every compound to a central ligand, typically the crystal structure ligand (CITE https://pubs.acs.org/doi/abs/10.1021/acs.jcim.9b00367). In this way the top-ranking examples can be readily identified and submitted to additional calculations in a second round. 
%
\subsection{Making predictions, understanding errors}
For prospective drug discovery applications there are several other considerations including understanding likely errors and taking selection bias into account. It is crucial when proposing compounds for synthesis to have some idea of the underlying error or uncertainty in the predictions. A retrospective assessment can give an indication of prospective performance for similar molecules (CITE https://pubs.acs.org/doi/abs/10.1021/acs.jcim.6b00220). Beyond this, several parameters provide useful indicators of performance, results suggest MBAR errors for perturbations greater than 0.3 kcal/mol can be indicative of inaccuracy~\cite{perez-benito2019predicting}. In addition, the hysteresis can be checked by comparing the difference for forward and reverse perturbations of the same structural change, or in the case of large maps of perturbations cycle closure hysteresis~\cite{wang2013modeling} indicates problematic perturbations involved in cycles connecting many compounds. Selection bias, as described above, can be problematic in prospective applications as there is normally an aim to focus on only a narrow range of predicted activity (i.e. the most active). Thus, correlation between prediction and subsequent experiment may lead to disappointment but corrections can be applied based on previous recommendations~\cite{abel2017critical}. 
%

@@

%
%
%
%%%%%%%%%%%%
% Step 1   %
%%%%%%%%%%%%
%
\section{What simulation protocol should I choose? -- Step 2}
\label{sec:step2}
Alchemical free energy calculations can be grouped into two main categories, ``absolute'' (\ref{fig:fig_absolute_thermodynamic_cycle}) and ``relative'' \footnote{The distinction is a bit of a misnomer, since both compute ratios of partition functions relative to another state, and neither computes an absolute free energy.}(\ref{fig:fig_binding_thermodynamic_cycle}), which differ in whether they compute properties for a single molecule (absolute) or compare properties of different, usually closely related, molecules (relative).
To use binding as a concrete example, in absolute binding free energy calculations, one computes the binding free energy of a ligand to an individual receptor relative to a standard reference concentration.
In contrast, in relative binding free energy calculations, one compares the binding free energy of two related inhibitors to determine the potency difference.
\subsection{Absolute and relative free energy calculations have some differences}
Many of the issues of setup and protocol for alchemical calculations are common, but some are different between absolute and relative calculations, so before treating the common elements we consider the protocol differences.

\subsubsection{Choices unique to relative free energy calculations}

@@

\subsubsection{Absolute free energy calculations must handle the standard state and use restraints}
\label{sec:standardstate-restraints}

@@

\subsection{Absolute and relative calculations must deal with some of the same issues}

\subsubsection{Structural definition of the bound state and weak binders}
\todo[inline, color={green!20}]{ASJM: This a bit waffly. What are the recommendations, of how to setup these restraints?}

@@

\subsubsection{Changes in net charge can be challenging/problematic.}

@@

\subsubsection{The importance of the alchemical pathway\label{sec:important_path}}
\todo[inline, color={green!20}]{ASJM: This a bit waffly. Can we address: what do softcore potentials actually look like (equation)? Give an example of a lambda switching function(equation)? MRS: adressed these questions to some extent.  How should you chose your lambda intermediates? What is the best practice here? I have conveniently provided a figure to help with the discussion.}
\todo[inline, color={red!40}]{LNN: write common principles alchemical path choice. MRS: mostly wrote this, LNN can comment on it,}
\todo[inline, color={red!40}]{AR: write absolute-specific section on  alchemical path choice}
\todo[inline, color={red!40}]{BA: write relative-specific section on  alchemical path choice}

@@

\subsubsection{What different sampling schemes exist and which one should I use?}
\todo[inline, color={green!20}]{ASJSM: I'll expand on this}
\ref{fig:fig_sampling_scheme} A:\cite{hedges2019biosimspace, song2019using } B\cite{aldeghi2015accurate, wang2015accurate,jiang2019computing} C:\cite{li2007simulated, tan2017optimally} D:\cite{aldeghi2018accurate}
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig8_sampl_scheme/Figure.pdf}
    \caption{\textbf{Four sampling strategies available in different software packages.} A: Multiple replicas in parallel at different lambda states. B: Hamiltonian replica exchange scheme. C: Single replica scheme sampling from all $\lambda$ states. D: Non-equilibrium sampling scheme.}
    \label{fig:fig_sampling_scheme}
\end{figure}

\subsubsection{How long should I run my simulation for and what information should be saved?}

@@

A simple, but effective, way of checking for bias is to compute the same property by multiple estimators. 
The uncertainty in the free energy, for example, has multiple ways to be estimated, e.g. through standard error propagation methods (including MBAR's estimator, which is based on the same principles as standard error propagation), through bootstrap methods, through multiple independent runs, etc. 
Independent of how the property is estimated, its important to remember that they are \textit{estimations of the property}, not the true underlying property itself. 
These estimators are usually consistent estimators, meaning they will converge to the true answer in the limit of sufficient sampling, not necessarily unbiased ones though.
As such, it is a good idea to subject different estimators to the same data to see if they yield either the same estimate (within error and bias), or if they fluctuate wildly. 
This is not a perfect method as some estimators, such as exponential averaging, will converge significantly more slowely, relative to more accurate estimators like MBAR. 
Therefore, it is a good idea to apply the estimators to different fractions of the data to see if the main estimator of free energy you have chosen is stable.

@@

\subsection{Detecting the boundary between equilibrated and production regions}
\label{sec:automatic-equilibration-detection}

@@

\subsection{Decorrelating samples for analysis}
\label{sec:decorrelating-samples}

@@

\subsection{Estimators for free energy differences}

@@

\subsubsection{Uncertainty estimation}

@@

In addition to statistical uncertainty and sampling, a variety of other factors can impact results from binding free energy calculations. In addition to the choice of initial configuration, results can depend on the choice of force field for the protein/receptor, water, and small molecuel(s), so rerunning calculations with different choices of force field can also be used to assess how sensitive results and conclusions are to these particular choices. Other factors, like system preparation (choice of protonation state, tautomer, counterion presence, salt concentration, etc.) can also substantially impact results~\cite{mobley2017predicting, mobley2017predictingb}, so unless modelers are confident they have these factors correct, sensitivity to these choices may also need to be examined.

\subsubsection{Are my simulations any good?}
One way of assessing reliability of the calculations is checking the phase space overlap between neighboring $\lambda$-windows~\cite{wu2005phasespace,wu2005phasespacea}. For this purpose, a so-called overlap matrix can be used. This is a $K\times K$ matrix, where $K$ is the number of simulated states, i.e. $\lambda$s. Sufficient overlap is important for reweighting estimators such as BAR or MBAR, but cannot help assess reliability of estimates, when using TI. 
These matrices are graphical representations of the phase space overlap, i.e. the average probability that a sample generated at state $j$ can be observed at state $i$. As this probability is computed considering the samples from all states (and not just the adjacent states), the values in each row and column add up to 1. In this analysis, the goal is to ensure every state has overlap with its neighbors in both directions -- so that off-diagonal elements are significantly larger than zero. Usually this means the matrix should be at least tridiagonal.

@@

\subsection{Best practices for data representation}

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and co-designed figures ~\ref{} and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.
JS: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.
MK: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.
DLM: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.
GT: Contributed to introduction and drug discovery sections, and helped edit the paper.
AR: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:step2}, and helped edit the paper.
MRS: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations.
LN: \todo[inline, color={red!20}{@Levi insert info here}
BA: \todo[inline, color={red!20}{@Bryce insert info here}
JM: \todo[inline, color={red!20}{@Julien insert info here}
JDC: \todo[inline, color={red!20}{@JDC insert info here}
HX: \todo[inline, color={red!20}{@Huafeng insert info here}
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.
